### 2021-04-07 pldi21/case-studies.tex
made code in text consistent with new fig1

First, the instructor defines a value \li{grades}
that records the grades for each student using a livelit, \li{\$dataframe},
that implements a tabular user interface. The formula bar
allows the selected cell to be filled with an arbitrary Hazel expression,
here a floating point expression that adds together individual problem scores,
one of which is expressed using another livelit,
\li{\$slider}.
The table itself displays not the expression itself but rather its value, \li{93.}, just as in a spreadsheet.

@@

\begin{lstlisting}[xleftmargin=0.2cm]
let grades = Dataframe (
  ["A1", "A2", "A3", "Midterm", "Final"],
  [("Alice", [24. +. 36. +. 33.,
              92., 83.5, 95., 88.]),
   ("Bob", [61., 64., 98., 70., 85.]),
   ("Carol", [75., 81., 73., 82., 79.]),
   (* ... *) ]) in
let averages = compute_averages grades weights in
let cutoffs = (.A 90., .B 80., .C 70., .D 60.) in
format_for_university
  (assign_grades averages cutoffs)
\end{lstlisting}

>>>>

First, the instructor defines a value \li{grades}
that records the grades for each student using a livelit, \li{\$dataframe},
that implements a tabular user interface. The formula bar
allows the selected cell to be filled with an arbitrary Hazel expression,
here a floating point expression that adds together individual problem scores,
one of which is expressed using another livelit,
\li{\$slider}.
The table itself displays not the expression itself but rather its value, \li{80.}, just as in a spreadsheet.

@@

\begin{lstlisting}[xleftmargin=0.2cm]
let q1_max = 36. in 
let grades = Dataframe (
  ["A1", "A2", "A3", "Midterm", "Final"],
  [("Andrew", [q1_max +. 24. +. 20.,
               92., 83.5, 95., 88.]),
   ("Cyrus", [61., 64., 98., 70., 85.]),
   ("David", [75., 81., 73., 82., 79.]),
   (* ... *) ]) in
let averages = compute_averages grades weights in
let cutoffs = (.A 86., .B 76., .C 67., .D 48.) in
format_for_university
  (assign_grades averages cutoffs)
\end{lstlisting}
